Whole-field total density measurements by Digital Image Correlation \thanks{Grants or other notes about the article that should go on the front page should be placed here. }

### 2020-02-18 Article/experimentsInFluids.tex
minor text

\noindent Looking at our forward model (\ref{eq:ForwardModel}), we know
\begin{enumerate}
	\item $n=n_0$ and $n=n_1$, the index of refraction of the reference image (filled with air) and the deformed image (filled with water); 
	\item $\underline{x}$, the coordinates on our image sensor; 
	\item $\underline{\Delta x}$, the measured displacement (after DIC). 
\end{enumerate}
The unknowns are the parameters $\underline{\alpha} = (a, b, c, L_m, x_p^0, y_p^0)$. We use the unit normal vector $\underline{\hat{n}}$ in our forward model; the parameters $a$, $b$ and $c$ are normalized. When optimizing we only need to know the ratio between these parameters since we normalize afterwards. We set $a=1$ and find those $b$ and $c$ that optimize our solution.

Since we have only five parameters to estimate and many measurements (each grid point yields a separate equation), we have an over-determined system. We use least-squares to find those $\underline{\alpha}$ that minimize the sum of squares of the residuals. The forward model depends nonlinearly on the parameters $\underline{\alpha}$ and the measurements $\underline{\Delta x}$. For each measurement $\underline{\Delta x}$ we have a measure of reliability, the correlation coefficient, which we use as a weight $w$ in the least squares procedure
\begin{equation}
\label{eq:calmin} 
	 \min_{\underline{\alpha}} \sum_i w_i \left(X(n_1, \underline{\alpha}, \underline{x}_i+\underline{\Delta x}_i) - X(n_0, \underline{\alpha}, \underline{x}_i)\right)^2, 
\end{equation}
with constraints (1) $L_c > 0$ and (2) $L_m \geq L_c + 2 L_g + L_t + L_s$, the experimental setup is in front of the camera; (3) $c < 0$, the unit normal vector of the planes points in the negative $z$-axis. Combining these constraints implies $d>0$. The sum is over all measured displacements.We use only the displacements in the $x$-direction, since that is the direction with the largest angles and thus largest signal. % The weights $w_i$ are $0$ when $CC < 0.8$ and $1$ otherwise.

>>>>

\noindent Looking at our forward model (\ref{eq:ForwardModel}), we know
\begin{enumerate}
	\item $n=n_0$ and $n=n_1$, the index of refraction of the reference image (filled with air) and the deformed image (filled with water); 
	\item $\underline{x}$, the coordinates on our image sensor; 
	\item $\underline{\Delta x}$, the measured displacement (after DIC). 
\end{enumerate}
The unknowns are the parameters $\underline{\alpha} = (a, b, c, L_m, x_p^0, y_p^0)$. We use the unit normal vector $\underline{\hat{n}}$ in our forward model; the parameters $a$, $b$ and $c$ are normalized. When optimizing we only need to know the ratio between these parameters since we normalize afterwards. We set $a = - 1$ and find those $b$ and $c$ that optimize our solution.

Since we have only five parameters to estimate and many measurements (each grid point yields a separate equation), we have an over-determined system. We use least-squares to find those $\underline{\alpha}$ that minimize the sum of squares of the residuals. The forward model depends nonlinearly on the parameters $\underline{\alpha}$ and the measurements $\underline{\Delta x}$. For each measurement $\underline{\Delta x}$ we have a measure of reliability, the correlation coefficient, which we use as a weight $w$ in the least squares procedure
\begin{equation}
\label{eq:calmin} 
	 \min_{\underline{\alpha}} \sum_i w_i \left(X(n_1, \underline{\alpha}, \underline{x}_i+\underline{\Delta x}_i) - X(n_0, \underline{\alpha}, \underline{x}_i)\right)^2, 
\end{equation}
with constraints (1) $L_c > 0$ and (2) $L_m \geq L_c + 2 L_g + L_t + L_s$, the experimental setup is in front of the camera; (3) $c < 0$, the unit normal vector of the planes points in the negative $z$-axis. Combining these constraints implies $d>0$. The sum is over all measured displacements. We use only the displacements in the $x$-direction, since that is the direction with the largest angles and thus largest signal. % The weights $w_i$ are $0$ when $CC < 0.8$ and $1$ otherwise.
